FictionEro - Affective Impact of Fiction

### 2025-12-02 analysis/analysis.qmd
analysis script

>>>>

#Individual models

m <- readRDS("models/individual_models/ModelArousal_1_task_1.rds")
m <- readRDS("models/individual_models/ModelArousal_1_task_2.rds")
m <- readRDS("models/individual_models/ModelArousal_1_task_3.rds")
m <- readRDS("models/individual_models/ModelArousal_1_task_4.rds")
m <- readRDS("models/individual_models/ModelArousal_1_task_5.rds")
m <- readRDS("models/individual_models/ModelArousal_1_task_6.rds")

m <- readRDS("models/individual_models/ModelArousal_2_task_1.rds")
m <- readRDS("models/individual_models/ModelArousal_2_task_2.rds")
m <- readRDS("models/individual_models/ModelArousal_2_task_3.rds")
m <- readRDS("models/individual_models/ModelArousal_2_task_4.rds")
m <- readRDS("models/individual_models/ModelArousal_2_task_5.rds")
m <- readRDS("models/individual_models/ModelArousal_2_task_6.rds")
